Bias and lability in the association between bumble bee visitation floral morphology along a montane-to-alpine elevation gradient

### 2021-02-05 writing/manuscript_v4.Rmd
developed ordination analysis
pretty much finalized analysis, almost done ms

---
title: "Bumble bee foraging bias"
author:
- Douglas B. Sponsler
- Fabrice Requier
- Katharina Kallnik
- Alice Claßen
- A. Fabienne Maihoff
- Ingolf Steffan-Dewenter
bibliography: refs.bib
output:
  pdf_document:
    fig_caption: yes
---

@@

## 3.3. Consequences of bias for niche relationships

>>>>

---
title: "Bias and lability in the association between bumble bee visitation floral morphology along a montane-to-alpine elevation gradient"
author:
- Douglas B. Sponsler
- Fabrice Requier
- Katharina Kallnik
- Alice Claßen
- A. Fabienne Maihoff
- Ingolf Steffan-Dewenter
bibliography: refs.bib
output:
  pdf_document:
    fig_caption: yes
---

@@

## 3.3. Consequences of bias for niche relationships
```{r fig4, echo = FALSE,  fig.cap = paste("Principal coordinates ordination of bumble bee visitation pooled across all samples.")}
knitr::include_graphics("../output/pcoa_aggregate.png")
```
